Cannibalism among the supermassive black holes

### 2018-06-01 paper.tex
Added most of Jerry's references to first paragraph of introduction.
Added most of Jerry's references to first paragraph of introduction, and added referenced papers to repository.

\section{Introduction}\label{sec:introduction}
What is the ultimate fate of the supermassive black holes (SMBH) resident at the centers of all massive galaxies?  For the galaxies themselves we know that mergers are frequent from the observed (ADD VAN DOKKUM PAPER) evolution of the size and mass of these systems.  But assuming that all galaxy mergers lead to SMBH mergers overpredicts the observations of gravitational waves from the pulsar timing arrays (PTAs) (\citet{2015ApJ...799..178K}, PRETONOS & OSTRIKER, SESANA, NATARJAN).  But we do not often see multiple SMBHs at the centers of massive ellipticals.  So, what does happen?  What we argue in this paper is that as a result of the N-body interactions among the infalling black holes some are ejected, some remain in extended orbits and some (the few most massive ones) do in fact merge but we do not exceed the PTA limits, and the orbiting ones should be detectable via their ability to accrete gas and emit radiation.

>>>>

\section{Introduction}\label{sec:introduction}
What is the ultimate fate of the supermassive black holes (SMBH) resident at the centers of all massive galaxies?  For the galaxies themselves we know that mergers are frequent from the observed (ADD VAN DOKKUM PAPER) evolution of the size and mass of these systems.  But assuming that all galaxy mergers lead to SMBH mergers overpredicts the observations of gravitational waves from the pulsar timing arrays (PTAs) (\citet{2015ApJ...799..178K}, \citet{2014ApJ...789..156M}, \citet{2008MNRAS.390..192S}, \citet{2013MNRAS.433L...1S}, \citet{2018ApJ...856...42S}, \citet{2009MNRAS.394.2255S}, NATARJAN).  But we do not often see multiple SMBHs at the centers of massive ellipticals.  So, what does happen?  What we argue in this paper is that as a result of the N-body interactions among the infalling black holes some are ejected, some remain in extended orbits and some (the few most massive ones) do in fact merge but we do not exceed the PTA limits, and the orbiting ones should be detectable via their ability to accrete gas and emit radiation.
